Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-08-22 manuscript.Rmd
Update manuscript.Rmd

author: 
  - name          : "Myrthe Veenman"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Wassenaarseweg 52, Leiden"
    email         : "myrthe.veenman@gmail.com"
  - name          : "Angelika Stefan"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author
  - name          : "Julia Haaf"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author

>>>>

author: 
  - name          : "Myrthe Veenman"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Wassenaarseweg 52, Leiden"
    email         : "myrthe.veenman@gmail.com"
  - name          : "Angelika M. Stefan"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author
  - name          : "Julia M. Haaf"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author
